Title Goes Here

### 2020-06-05 analysis/paper/paper.Rmd
aaaaa

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership they remain underrepresented in peer-reviewed journals. @tushingham2017peer examined authorship gender trends in 1,599 papers in three journals, _Journal of California and Great Basin Anthropology/Journal of California Archaeology_ (JCGBA/JCA), _California Archaeology_ (CA) and a non-peer reviewed _Proceedings_ of the Society for California Archaeology (PSCA). In a total of 2,617 authors, 844 (32.3%) were women, 1,762 (67.3%) were men, and 11 (0.4%) were gender unknown/ambiguous [@tushingham2017peer]. They found significant increases in the proportion of female lead authors over time in JCGBA/JCA and PSCA, but not in CA, perhaps because of the shorter publishing period for this journal [@tushingham2017peer]. This similar trend of a gender gap in archaeology can also be seen in women's pay [@vanderwarker2018ucsb]. In the University of California, Santa Barbara Gender Equity Project,@vanderwarker2018uscb report an imbalance in pay rates, for example, women make a greater proportion of people paid less \$60,000 and men outnumber women in salary brackets greater than \$60,000. (@vanderwarker2018uscb).

<!-- summarise studies of citation practices that show a gap -->

>>>>

@bardolph2018controlling has examined data from 2007 to 2017 about the membership in 
the Society of California Archaeology (SCA) conference, the lead-authors of peer-reviwed journal _Journal of Californial and Great Basin Anthropology_ (JCGBA), and _California Archaeology_ (CA). @bardolph2018controlling noted that the women's presentation rate is consistent with their membership rates in SCA, and that women's participation rate in 2017 was finally able to exceed that of men's. Although women is more actively participating in SCA, the same is not shown in terms of the lead-authorship of JCGBA and CA [@bardolph2018controlling]. Throughout the majoirty of time in the period collected, the lead-authorship of JCGBA is obviously skewed towards men and only 34% of them are women. A greater difference between men and women lead-authorship can be seen in CA, in 2009 there was no women lead-authors at all and overall only 23% of the publichsed papers of CA are women lead-authors [@bardolph2018controlling].

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership they remain underrepresented in peer-reviewed journals. @tushingham2017peer examined authorship gender trends in 1,599 papers in three journals, _Journal of California and Great Basin Anthropology/Journal of California Archaeology_ (JCGBA/JCA), _California Archaeology_ (CA) and a non-peer reviewed _Proceedings_ of the Society for California Archaeology (PSCA). In a total of 2,617 authors, 844 (32.3%) were women, 1,762 (67.3%) were men, and 11 (0.4%) were gender unknown/ambiguous [@tushingham2017peer]. They found significant increases in the proportion of female lead authors over time in JCGBA/JCA and PSCA, but not in CA, perhaps because of the shorter publishing period for this journal [@tushingham2017peer]. This similar trend of a gender gap in archaeology can also be seen in women's pay [@vanderwarker2018ucsb]. In the University of California, Santa Barbara Gender Equity Project,@vanderwarker2018uscb report an imbalance in pay rates, for example, women make a greater proportion of people paid less \$60,000 and men outnumber women in salary brackets greater than \$60,000. [@vanderwarker2018uscb].

One common flaw that often exists in the study of genders from lead-authorships is the fact that most are done by the method of predicting the gender based on the author's first name, as noted by @heathwrites, she has recently conducted a survey that directly asks the archaeologists that published in some journals for their self-identifications of gender, race/ethnicity and sexual orientation. @heathwrites has used the data she gathered to compare it to previously done studies on similar topic of lead-authorships in jounals such as, _Advances in Archaeological Practice_ (AAP), _American Antiquity_ (AAQ), _Ancient Mesoamerica_ (AM), _Historical Archaeology_ (HA), _Journal of Archaeological Method and Theory_ (JAMT), _Journal of Archaeological Research_ (JAaR), _Journal of Field Archaeology_ (JFA), and _Latin American Antiquity_ (LAQ). From the comparison, @heathwrites found that there is a higher number of women publishing in the field of archaeology than it is shown in previous studies in the same publications, which is most likely a result of change overtime, and that most journals is slowly reaching to gender parity.

Inside the field of archaeology there are still a variation of topics to study, which @mallia2009opposite focuses on in her paper using 222 articles from journals of _Revista Espanola de Antropologia Americana_ (REAA) and 206 articles from _Anales del Museo de America_ (AMA), over a time span of 1993 to 2007. @mallia2009opposite found that there seems to be some topics that are more commonly studied/published, for example, when dividing the topics into Pre-Columbian, Contact, Colonial and Republican, in REAA there is more collboration with American writers and those that do frequent field work in South America and this corresponded with pre-Columbian as the dominant time span then followed by Republican, while AMA shows a dominant in the time span of Colonial periods which is likely due to the author's study of collections of arts and records from museum. Although the article only focused on topics within the field of arhcaeology and its distribution, we are interested in whether gender can be a factor in terms of what kinds of topics are more frequently studied.
<!-- summarise studies of citation practices that show a gap -->
